<small> Supplementary materials for the main submission entitled - <br><br> Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-11-16 paper/paper-supplementary.Rmd
making notations consistent with paper - continue part 2

bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    MonashEBSTemplates::workingpaper:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points. The number of cyclic granularities considered in the display (at once) is $m$. Consider cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$. For $m=1$, only one of $A$ or $B$ is plotted at once and a _panel_ refers to a display of distributions of $v$ across $J$ or $K$ levels on the x-axis. For $m=2$, the distribution display of $v$ with $A$ placed across x-axis and $B$ across facets is referred to as a $(J, K)$ _panel_ ($J$ x-axis levels and $K$ facet levels). The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or between-facets as seen in Figure 4 of the main paper. The tuning parameter, used to put relative weight-age to the pairwise distances within and between facets is denoted by $\lambda$. Let the four elementary designs be $D_{null}$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$. Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across $A$. Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$. The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$), where $\omega$ denotes the increment in mean. Table \ref{tab:explain-design} shows an example of how designs are defined for a $(2, 3)$ panel using $\omega = 3$. $nx$ and $nfacet$ denotes the number of categories placed on x-axis and facets respectively. $wpd_{raw}$ and $wpd$ denote the raw and normalized weighted pairwise distances.

@@

raw_table <- bind_cols(x = x, 
                       facet = facet, 
                       null = null,
                       vary_f = vary_f, 
                       vary_x = vary_x, 
                       vary_all = vary_all) %>% 
  tibble() 
names(raw_table) = c("x levels", "facet levels", "$D_{null}$",  "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
raw_table %>% 
  kable(format = "latex",
    booktabs = TRUE, 
    escape = FALSE,
    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$ and $\\omega=3$.") %>% kable_styling()
```

@@

For $m=1$, pairwise distances could be defined only between different categories of the cyclic granularity considered. So no tuning parameter is applicable for this case. For $m=2$, $\lambda$ might impact $wpd_{raw}$ differently depending on the value of $\omega$ and different values of $nx$, $nfacet$ and designs. The following simulation study sees the impact of $\lambda$ for different $\omega$, $nx$, $nfacet$ and designs.

@@

Observations are generated from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $wpd_{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $D_{var_x}$ and $D_{var_f}$ for $\omega = \{1, 8\}$  to observe how the value of $wpd_{raw}$ changes for different designs. Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.

<!-- and the values of $wpd$ is computed for all these different values of the variables $nx$, $nfacet$, $\lambda$ and $\omega$ under two different designs $D_{var_x}$ and $D_{var_f}$ .  -->

@@

Figure \ref{fig:tuning-oneomega} shows how the value of $wpd$ changes for $\lambda = {0.1, 0.2, \dots, 0.9}$ for the two different designs $D_{var_x}$ and $D_{var_f}$ for two values of increment in mean $\omega = {1, 8}$. For a lower value of $\omega$, the two designs intersect at $\lambda > 0.7$ and for a higher $\omega$, the two designs intersect at $\lambda =  0.5$. The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for $D_{var_f}$. \noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$. It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$ and for $\omega$ ($\omega <= 4$), designs interact between $\lambda = [0.6,0.75]$. Hence, $\lambda = 0.67$ is used for the rest of the paper, which is an average of the range of values $\lambda$ can take in order to have equal or more weightage for the within-facet distances.

```{r tuning-oneomega, fig.cap = " $wpd_{raw}$ from two designs are plotted for different values of $\\lambda$ $nx$ and $nfacet$. For $\\omega = 1$, the designs intersect for $0.6<\\lambda<=0.75$, whereas for higher omega, design intersects at $\\lambda = 0.5$."}
knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
```

```{r tuning-parameter-inter, fig.cap ="The point of intersection of $wpd_{raw}$ values under the designs $D_{var_f}$ and $D_{var_x}$ are plotted across different $\\omega$ and $\\lambda$. For most panels it is observed that a common value of $\\lambda$ for which the designs interact is $0.5$ for $\\omega >= 4$, which implies any value greater than $0.5$ could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances. The value of $\\lambda$ is higher for  $\\omega<4$ could be anywhere between 0.6 and 0.75."}
knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
```

@@

The following simulation study sees the impact of different underlying distributions on $wpd_{raw}$ for different $nx$ and $nfacet$ before and after performing Normal Quantile Transformation.

@@

Observations are generated from N(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $wpd_{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 2) NQT.

@@

Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of $wpd_{raw}$ for a Gamma(0.5,1), Gamma(2,1) before NQT. It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel. Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions after performing NQT. It is observed that within each panel, the distributions of the $wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels. Similar observations could be made in Figure \ref{fig:normal-diff-quantrans} for different underlying normal distributions  N(0,1), N(5,1) and N(0,5). This implies, NQT has atleast been able to make the location and scale of the distribution of $wpd_{raw}$ same for different underlying distributions.

<!-- Since the measure $wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution. To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like. -->

@@

\noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high. $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories. This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution. Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed. The values of $wpd$ is obtained for each of the panels. $wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.

@@

Figure \ref{fig:nxbyfacet-ridge-N01-onegran} shows ridge plots of $wpd_{raw}$ for an underlying N(0,1) distribution. For each panel, it could be seen that the location shifts to the right for increasing x levels. Across each panel, the scale of the distribution seems to change for low/moderately from lower values  to higher values of $nx$ and left tails are longer for lower facet levels.

@@

\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$. That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.

<!-- Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values -->
<!-- of $wpd$ is obtained for each of the panels. The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ . Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.    -->

@@

Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets. The right-ward shift in location can be clearly observed from all figures.

@@

This section shows results from the different approaches of adjusting for the number of comparisons. Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$. In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panels.

<!-- \noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high. $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories. This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution. Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed. The values of $wpd$ is obtained for each of the panels. $wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation. -->

@@

Figure \ref{fig:one-gran-nxnyfacet} and \ref{fig:norm} show the normalized ${wpd}$ for $m=1$ and $m=2$ respectively. The location and scale of the distribution of ${wpd}$ is similar for increasing values of $nx$ or $nfacet$. Due to heavy computational load, $wpd_{perm}$ for few panels with very high value of $nx$ or $nfacet$ are not computed.

```{r one-gran-nxnyfacet, fig.cap="Distribution of $wpd_{perm}$ are shown for different levels for $m=1$ under the null design. The distribution for different panels have similar location and scale."}
include_graphics(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/figs/nxbyfacet_ridge_wpd_N01.png"))
```

```{r norm, fig.cap = "Distribution of $wpd_{perm}$ are shown for different levels for $m=2$ under the null design. The distribution for different panels have similar location and scale."}
G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

@@

For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$. For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatter plot of $wpd_{raw}$ against different values of $nx$ and $nfacet$ and also the display of residuals from the model. Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$ and $nfacet$. Tables \ref{tab:tab-modelsm1} and \ref{tab:tab-models} show the GLM results for $m=1$ and $m=2$ respectively. All of these jointly show that the residuals from the model are independent of the number of comparisons. The location and scale of the distribution of $wpd_{glm}$ is similar for higher levels and distinctly different for lower levels.

@@

bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% 
  mutate(estimate = round(estimate, 2),
         std.error = round(std.error, 3),
         statistic = round(statistic, 2),
         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")

@@

```{r glm-horizontal-onegran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=1$. Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
knitr::include_graphics(here("paper/figs/G21_horizontal.png"))
```

```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=1$. Both shape and location of the distributions are different for lower $nx$ than for higher $nx$."}
G21_glm_m1 <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
  )
  )
  ),
  wpd_glm_scaled = ((wpd_glm*261)))

@@

tidy_obs %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for different underlying distribution.")
```

@@

```{r glm-horizontal-twogran, fig.cap = "Residuals from the model is plotted across different $nx$ and $nfacet$. Residuals seem to be independent of $log(nx*nfacet)$ and have been defined as $wpd_{glm}$ in the paper."}

@@

# broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")

@@

```{r glm-horizontal-twogran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=2$. Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
knitr::include_graphics(here("paper/figs/G21_horizontal_m2.png"))
```

```{r wpd-glm-dist, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=2$. Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
G21_glm <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
  )
  )
  ),
  wpd_glm_scaled = ((wpd_glm*320)))

>>>>

bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    MonashEBSTemplates::workingpaper:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    includes:
      in_header: preamble.tex
---

@@

Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points. The number of cyclic granularities considered in the display (at once) is $m$. Consider cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, \nx\}$ and $B = \{b_k: k = 1, 2, \dots, \nf\}$. For $m=1$, only one of $A$ or $B$ is plotted at once and a _panel_ refers to a display of distributions of $v$ across $J$ or $K$ levels on the x-axis. For $m=2$, the distribution display of $v$ with $A$ placed across x-axis and $B$ across facets is referred to as a $(\nx, \nf)$ _panel_ ($\nx$ x-axis levels and $\nf$ facet levels). The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or between-facets as seen in Figure 4 of the main paper. The tuning parameter, used to put relative weight-age to the pairwise distances within and between facets is denoted by $\lambda$. Let the four elementary designs be $\\Dnull$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $\\Df$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$. Similarly, $\\Dx$ denotes the set of designs where difference is observed only across $A$. Finally, $\\Dfx$ denotes those designs for which difference is observed across both $A$ and $B$. The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $\\Dx$) and $\mu_{.k} = \mu + k\omega$ (for design $\\Df$), where $\omega$ denotes the increment in mean. Table \ref{tab:explain-design} shows an example of how designs are defined for a $(2, 3)$ panel using $\omega = 3$. $\\nx$ and $\\nf$ denotes the number of categories placed on x-axis and facets respectively. $\wpdsub{raw}$ and $\wpd$ denote the raw and normalized weighted pairwise distances.

@@

raw_table <- bind_cols(x = x, 
                       facet = facet, 
                       null = null,
                       vary_f = vary_f, 
                       vary_x = vary_x, 
                       vary_all = vary_all) %>% 
  tibble() 
names(raw_table) = c("x levels", "facet levels", "$\\Dnull$",  "$\\Df$", "$\\Dx$", "$\\Dfx$" )
raw_table %>% 
  kable(format = "latex",
    booktabs = TRUE, 
    escape = FALSE,
    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$ and $\\omega=3$.") %>% kable_styling()
```

@@

For $m=1$, pairwise distances could be defined only between different categories of the cyclic granularity considered. So no tuning parameter is applicable for this case. For $m=2$, $\lambda$ might impact $\wpdsub{raw}$ differently depending on the value of $\omega$ and different values of $\\nx$, $\\nf$ and designs. The following simulation study sees the impact of $\lambda$ for different $\omega$, $\\nx$, $\\nf$ and designs.

@@

Observations are generated from N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $\wpdsub{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $\\Dx$ and $\\Df$ for $\omega = \{1, 8\}$  to observe how the value of $\wpdsub{raw}$ changes for different designs. Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $\nx\ \in \{2, 3, 5, 7, 14, 20\}$, $\nf\ \in \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.

<!-- and the values of $\wpd$ is computed for all these different values of the variables $\\nx$, $\\nf$, $\lambda$ and $\omega$ under two different designs $\\Dx$ and $\\Df$ .  -->

@@

Figure \ref{fig:tuning-oneomega} shows how the value of $\\wpd$ changes for $\lambda = {0.1, 0.2, \dots, 0.9}$ for the two different designs $\\Dx$ and $\\Df$ for two values of increment in mean $\omega = {1, 8}$. For a lower value of $\omega$, the two designs intersect at $\lambda > 0.7$ and for a higher $\omega$, the two designs intersect at $\lambda =  0.5$. The value of $\wpd$ increases with $\lambda$ for $\\Dx$ and decreases with increasing $\lambda$ for $\\Df$. \noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$. It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$ and for $\omega$ ($\omega <= 4$), designs interact between $\lambda = [0.6,0.75]$. Hence, $\lambda = 0.67$ is used for the rest of the paper, which is an average of the range of values $\lambda$ can take in order to have equal or more weightage for the within-facet distances.

```{r tuning-oneomega, fig.cap = " $\\wpdsub{raw}$ from two designs are plotted for different values of $\\lambda$ $\\nx$ and $\\nf$. For $\\omega = 1$, the designs intersect for $0.6<\\lambda<=0.75$, whereas for higher omega, design intersects at $\\lambda = 0.5$."}
knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
```

```{r tuning-parameter-inter, fig.cap ="The point of intersection of $\\wpdsub{raw}$ values under the designs $\\Df$ and $\\Dx$ are plotted across different $\\omega$ and $\\lambda$. For most panels it is observed that a common value of $\\lambda$ for which the designs interact is $0.5$ for $\\omega >= 4$, which implies any value greater than $0.5$ could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances. The value of $\\lambda$ is higher for  $\\omega<4$ could be anywhere between 0.6 and 0.75."}
knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
```

@@

The following simulation study sees the impact of different underlying distributions on $\wpdsub{raw}$ for different $\\nx$ and $\\nf$ before and after performing Normal Quantile Transformation.

@@

Observations are generated from N(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $\wpdsub{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 2) NQT.

@@

Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of $\wpdsub{raw}$ for a Gamma(0.5,1), Gamma(2,1) before NQT. It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel. Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $\wpd$ under same underlying distributions after performing NQT. It is observed that within each panel, the distributions of the $\wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels. Similar observations could be made in Figure \ref{fig:normal-diff-quantrans} for different underlying normal distributions  N(0,1), N(5,1) and N(0,5). This implies, NQT has atleast been able to make the location and scale of the distribution of $\wpdsub{raw}$ same for different underlying distributions.

<!-- Since the measure $\wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution. To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like. -->

@@

\noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high. $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories. This design corresponds to $\\Dnull$ as each combination of categories in a panel are drawn from the same distribution. Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed. The values of $\wpd$ is obtained for each of the panels. $wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.

@@

Figure \ref{fig:nxbyfacet-ridge-N01-onegran} shows ridge plots of $\wpdsub{raw}$ for an underlying N(0,1) distribution. For each panel, it could be seen that the location shifts to the right for increasing x levels. Across each panel, the scale of the distribution seems to change for low/moderately from lower values  to higher values of $\\nx$ and left tails are longer for lower facet levels.

@@

\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$. That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.

<!-- Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values -->
<!-- of $\wpd$ is obtained for each of the panels. The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $\\Dnull$ . Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed.    -->

@@

Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $\wpdsub{raw}$ with $\\nx$ as facets, $\\nf$ as facets and the density plot of $\wpdsub{raw}$ with $\\nx$ on the x-axis and $\\nf$ on the facets. The right-ward shift in location can be clearly observed from all figures.

@@

This section shows results from the different approaches of adjusting for the number of comparisons. Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$. In place of $\wpdsub{raw}$, $\wpdsub{perm}$, $wpd_{glm}$ and $\wpd$ is computed for all panels.

<!-- \noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high. $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories. This design corresponds to $\\Dnull$ as each combination of categories in a panel are drawn from the same distribution. Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed. The values of $\wpd$ is obtained for each of the panels. $wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation. -->

@@

Figure \ref{fig:one-gran-nxnyfacet} and \ref{fig:norm} show the normalized ${wpd}$ for $m=1$ and $m=2$ respectively. The location and scale of the distribution of ${wpd}$ is similar for increasing values of $\\nx$ or $\\nf$. Due to heavy computational load, $\wpdsub{perm}$ for few panels with very high value of $\\nx$ or $\\nf$ are not computed.

```{r one-gran-nxnyfacet, fig.cap="Distribution of $\\wpdsub{perm}$ are shown for different levels for $m=1$ under the null design. The distribution for different panels have similar location and scale."}
include_graphics(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/figs/nxbyfacet_ridge_wpd_N01.png"))
```

```{r norm, fig.cap = "Distribution of $\\wpdsub{perm}$ are shown for different levels for $m=2$ under the null design. The distribution for different panels have similar location and scale."}
G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

@@

For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $\wpdsub{raw}$ against different values of $\\nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $\\nx$. For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatter plot of $\wpdsub{raw}$ against different values of $\\nx$ and $\\nf$ and also the display of residuals from the model. Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $\\nx$ and $\\nf$. Tables \ref{tab:tab-modelsm1} and \ref{tab:tab-models} show the GLM results for $m=1$ and $m=2$ respectively. All of these jointly show that the residuals from the model are independent of the number of comparisons. The location and scale of the distribution of $wpd_{glm}$ is similar for higher levels and distinctly different for lower levels.

@@

bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% 
  mutate(estimate = round(estimate, 2),
         std.error = round(std.error, 3),
         statistic = round(statistic, 2),
         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")

@@

```{r glm-horizontal-onegran1, fig.cap = "$\\wpdsub{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=1$. Residuals seem to be independent of $\\nx$ and have been defined as $wpd_{glm}$."}
knitr::include_graphics(here("paper/figs/G21_horizontal.png"))
```

```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $\\nx$ for $m=1$. Both shape and location of the distributions are different for lower $\\nx$ than for higher $\\nx$."}
G21_glm_m1 <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
  )
  )
  ),
  wpd_glm_scaled = ((wpd_glm*261)))

@@

tidy_obs %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for different underlying distribution.")
```

@@

```{r glm-horizontal-twogran, fig.cap = "Residuals from the model is plotted across different $\\nx$ and $\\nf$. Residuals seem to be independent of $log(nx*nfacet)$ and have been defined as $wpd_{glm}$ in the paper."}

@@

# broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons.")

@@

```{r glm-horizontal-twogran1, fig.cap = "$\\wpdsub{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=2$. Residuals seem to be independent of $\\nx$ and have been defined as $wpd_{glm}$."}
knitr::include_graphics(here("paper/figs/G21_horizontal_m2.png"))
```

```{r wpd-glm-dist, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $\\nx$ for $m=2$. Both shape and scale of the distributions are different for lower $\\nx$ than for higher $\\nx$."}
G21_glm <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
  )
  )
  ),
  wpd_glm_scaled = ((wpd_glm*320)))
